---
title: "Assignment 7: Collaborative Coding"
output: html_document
---

&nbsp;

```{r setup, include=FALSE}
library(dplyr)
library(plotly)
library(knitr)

source("scripts/summary-information.R")
source("scripts/chartfile1.R")
source("scripts/chartfile2.r")

data <- read.csv("https://raw.githubusercontent.com/INFO-498F/a7-survey-data/master/intro_survey_data.csv")

knitr::opts_chunk$set(echo = TRUE)
```

```{r Info, echo=FALSE, message=FALSE, warning=FALSE}
info <- info_function(data)

total <- info$num_of_freshman + info$num_of_sophomores + info$num_of_junior + info$num_of_senior

pc <- function(x) {
  return(round(x/total * 100))
}

sp <- pc(info$num_of_sophomores)
major <- pc(info$num_applying_to_major)
xp <- pc(info$num_moderate_programming_exp)
os <- pc(info$num_windows_users)
pet <- pc(info$num_dog_person)
twelfth <- pc(info$num_seahawks_fan + info$num_major_seahawks_fan)
```

### Highlights from the survey

This is a report of data collected from `r total` students from the winter 2016 INFO 498F class who took a survey. Based on the results, `r sp`% are sophomores, `r major`% want to be Informatics majors, `r xp`% have moderate programming experience, `r os`% use Windows machines, `r pet`% are dog people, and `r twelfth`% are Seahawks fans.

&nbsp;

```{r Charts, echo=FALSE, message=FALSE, warning=FALSE}
chart1 <- make_INFOinterest_chart(data)
chart2 <- make_bar_chart(data)
```

#### Here's a chart displaying the distribution of the surveyed students interest in the Informatics major and the type of operating system they use.

&nbsp; 

`r chart1` 

&nbsp;

#### ... and here's another chart displaying the distribution of the class standing from those who completed the survey.

&nbsp; 

`r chart2`
